### 2023-03-27 uvp6_part.qmd
Revue du paragraphe de préambule

Building the zooplankton classification model for the UVP6 was the first task of my PhD. To be honest, I knew nothing about machine learning before I started this so I spent the first three weeks reading a nice machine learning book in the corner of my team leader's office. To be even more honest, I basically knew nothing about zooplankton either. I think it is time to admit it.

In machine learning, the no free lunch theorem [@Wolpert1996-hw] states that if you do not make any assumption about your data, then there is no model that is a priori guaranteed to work better [@Geron2019-is]. In other words, it means that you need to get your hands dirty to find a model that works. The first step consisted in developing a full data processing pipeline using UVP5 images. The aim was to be prepared for the UVP6 image data set (not ready at that time) to train the true final classification model. To this end, I developed a python package called [UVPec](https://github.com/ecotaxa/uvpec) that is able to create a full classification model based on image folders with labeled particle/zooplankton images and some hyperparameters (e.g. learning rate). It really made my life easier when I got the final UVP6 data set and it saved me a lot of time.

In the end, I am rather satisfied with the results. Classifying zooplankton is already difficult for human operators (at least, for me) so building a model to automatically classify them is one challenge but adding technical and energy constraints to it was the ice on the cake. Below is the first draft of a publication on the classification model.

>>>>

Building the zooplankton classification model for the UVP6 was the first task of my PhD. I knew nothing about machine learning before I started, so I spent the first three weeks reading a machine learning book to get familiar with the concepts. To be even more honest, I also knew nothing about zooplankton either, so there was something else to learn.

In machine learning, the "no free lunch theorem" [@Wolpert1996-hw] states that if you do not make any assumption about your data, then there is no model that is a priori guaranteed to work better [@Geron2019-is]. In other words, it means that you need to get to know your data and your hands dirty to find a model that works. The first step consisted in developing a full data processing pipeline for UVP5 images. The aim was to be prepared for the UVP6 image data set (which was not ready at that time) to train the true, final, classification model. To this end, I developed a python package called [UVPec](https://github.com/ecotaxa/uvpec) that is able to create a full classification model based on image folders with labeled particle/zooplankton images and some hyperparameters (e.g. learning rate). It made my life easier when I got the final UVP6 data set and should serve other future users in the same way.

Classifying zooplankton on UVP images is difficult for human operators so building a model to automatically classify them is already a challenge, but adding technical and energy constraints to it was the icing on the cake. Below is the first draft of a publication on the classification model.
